\unnumberedchapter{Glossary} 
\chapter*{Glossary} 

% Break up this table into several ones if it takes up more than one page
\begin{center}
\begin{longtable}{r p{0.58 \textwidth}}

American Library Association (ALA) \cite{glossary2013} & The largest and oldest library organization in the world, with the mission of promoting library services and librarianship.  \\ 

branch (Github) & the repository file system. The repository automatically comes with a "main" branch, and contributors can create multiple and switch between them on the local and Github copy of the repository for best organization of information. \\ 

branch library \cite{glossary2013} & A library (3) within a library system (2) but separate from the central library (2), with no less than a basic collection (5) of materials , a regular staffing level, and an established service schedule. \\

bugs & issues in the code where it does not function as intended. \\ 

circulation & the movement of information, usually physical information such as books when in the context of the physical library.  \\

code & computer code which is written to be read by the compiler for that languages and the computer itself. \\

commit & creating using the "git commit" command \cite{gitdocs} in the CLI, this is an encapsulation of the changes made in the local repository. \\

commit log & on Github, the list of history of all commits to the given branch of the Github repository. The commits are organized by day and listed in the order which they were created with the "git commit" command using Git in the CLI. \\

\end{longtable}
\end{center} 

\begin{center}
\begin{longtable}{r p{0.58 \textwidth}}

CONTRIBUTING.md & a file in the Github repository which contains the process of contributing to the given software and interacting in the software community. These guidelines may also be stored in documentation of the project, but it is best practice for there to be visible contributing guidelines. \\

dependencies & in a software, the other software which the given one relies on in order to carry out it's full intended function. They support functionality that is not local to the software.  \\

documentation & written information for contributors and users of a project, which describes the functionality of code and the processes of contributing to the project. \\

fork & a full copy of the main repository on Github at the point at which it is made, this includes new blank versions of the tabs, aside from the commits on the code tab, which note how many commits ahead/behind the fork is from the main branch of the main repository. \\

FOSS (Free Open Source Software) \cite{gnuphilosophy} & “Free software” means software that respects users' freedom and community. Roughly, it means that the users have the freedom to run, copy, distribute, study, change and improve the software. Thus, “free software” is a matter of liberty, not price. \\

Github & Owned by Microsoft, a platform which includes repositories that have been and contribute to be essential to the organization of FOSS communities and the projects they work on. \\

Github Actions & one of the features in a Github repository, which allow developers to automate administrative tasks in the repository, such as bots which change the status of PRs with no activity in a certain amount of time from open to closed. \cite{pandasrepo} \\

Git Flow & the process using Git commands and features in the repository to contribute to Github. This is considered a best practice in using Github. \\

hackathons/Hacktoberfest & Community events where individuals or teams of individuals work on software projects within a certain amount of time. Hacktoberfest is specifically during the month of October and involves contributing to open source software, often through Github. \\


Issue Tracker & the second tab to the right of the Code tab in a Github repository, where the community can raise changes that should be made in the project and hold community discussions. \\

local machine/repository & the copy of the repository which is on a user or contributor's computer, verses the remote one online on Github. \\

library & "1. A collection (5) of materials in various formats (4) organized to provide physical, bibliographic, and intellectual access to a target group , with a staff trained to provide services and programs related to the information needs of the target group . 2. A building or structure that houses such a collection (5). 3. The institution that manages such a collection (5). 4. A private collection (3) of materials , often owned by an individual, such as books , sound discs, or videodiscs." \cite{glossary2013} \\

library catalog & register of everything in the physical library \\

library database & the online search-able database of the entire library \\

Lots Of Copies\\Keeps Stuff Safe (LOCKSS) & the idea that the more copies of information that exist, the less likely it is for that information to be permanently lost. \\

maintainers & contributors who carry out administrative actions for the project and project community. \\

Markdown & a markup language used in .md files, such as the README and other documentation in Github repositories.\\

pull & using the "git pull" \cite{gitdocs} in the CLI to retrieve the most up-to-date version of the repository file system from the remote repository on Github. \\

pull request & the last step of Git Flow, which includes considering merging the commits from a branch or fork into the main branch of the main project repository. \\

push & using the "git push" \cite{gitdocs} command in the CLI to move the commit from the local repository to the remote repository on Github. \\ 


project board & On Github, the tab which allows contributors and maintainers to organize issues and tasks into columns to track the completion of work in a repository, often toward a specific overall goal. \\

README.md & the central piece of documentation in a repository, on the main page of the Code tab in a repository. Including a README is not automatic with the repository template, but creating one is considered best practice. \\

squashed commits & when the changes within two or more commits are all put into one commit. \\ 

repository & the data structure which holds information on Github, which is typically software projects, although it is not limited to this. \\

remote repository & the online repository on Github. \\

\end{longtable}
\end{center} 